\documentclass[11pt]{res} % default is 1.0 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{multicol}
% \usepackage{times}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}

\usepackage[UKenglish]{datetime}

\begin{document} 
{\centering \Large \bf JAVIER A. CONCHA, Ph.D.\par} % the \\[12pt] adds a blank line after name
\vspace{0.2in}                                         
\begin{multicols}{2}
{\raggedright Postdoctoral Research Fellow\\Institute of Marine Science (ISMAR)\\ National Research Council of Italy (CNR)\\ ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\}
{\raggedleft Via Acqui 10, int. 8A\\Roma, RM 00183, Italy\\Mobile: +39 347 752 2354\\Email: Javier.Concha@artov.ismar.cnr.it\\}
\end{multicols}
\vspace{-0.4in} 
\hrulefill
\begin{resume}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.3in}   
\section{PUBLICATIONS -- PEER REVIEWED}
\vspace{0.05in}
{\bf Concha, J.A.}, Bracaglia, M., Brando, V.E., {\it Assessing the influence of different validation protocols on Ocean Colour match-up analyses}, Remote Sensing of Environment, {\bf 2021}.  Vol. 259. (\url{https://doi.org/10.1016/j.rse.2021.112415}).

Giardino, C., Bresciani, M., Braga, F., Fabbretto, A., Ghirardi, N., Pepe, M., Gianinetto, M., Colombo, R., Cogliati, S., Ghebrehiwot, S., Laanen, M., Peters, S., Schroeder, T., {\bf Concha, J.A.}, Brando, V.E., {\it First Evaluation of PRISMA Level 1 Data for Water Applications}, Sensors. {\bf 2020}. Vol. 20(16):4553. (\url{https://doi.org/10.3390/s20164553}).

{\bf Concha, J.A.}, Mannino, A., Franz, B. $\&$ Kim, W., {\it Uncertainties in the Geostationary Ocean Color Imager (GOCI) Remote Sensing Reflectance for Assessing Diurnal Variability of Biogeochemical Processes}, Remote Sensing, {\bf 2019}. Vol. 11(3):295 (\url{https://doi.org/10.3390/rs11030295}).

{\bf Concha, J.A.}, Mannino, A., Franz, B., Bailey, S., $\&$ Kim, W., {\it Vicarious Calibration of GOCI for SeaDAS Ocean Color Retrieval}, International Journal of Remote Sensing, {\bf 2018}. Vol. 40, issue 10: p. 3984-4001. (\url{https://doi.org/10.1080/01431161.2018.1557793}).

{\bf Concha, J.A.} $\&$ Schott, J., {\it Retrieval of color producing agents in Case 2 waters using Landsat 8}, Remote Sensing of Environment, {\bf 2016}. Vol. 185: p. 95-107. (\url{https://doi.org/10.1016/j.rse.2016.03.018})

Muller‐Karger, F.E., Hestir, E., Ade, C., Turpie, K., Roberts, D.A., Siegel, D., Miller, R.J., Humm, D., Izenberg, N., Keller, M., Morgan, F., Frouin, R., Dekker, A.G., Gardner, R., Goodman, J., Schaeffer, B., Franz, B.A., Pahlevan, N., Mannino, A.G., {\bf Concha, J.A.}, Ackleson, S.G., Cavanaugh, K.C., Romanou, A., Tzortziou, M., Boss, E.S., Pavlick, R., Freeman, A., Rousseaux, C.S., Dunne, J., Long, M.C., Klein, E., McKinley, G.A., Goes, J., Letelier, R., Kavanaugh, M., Roffer, M., Bracher, A., Arrigo, K.R., Dierssen, H., Zhang, X., Davis, F.W., Best, B., Guralnick, R., Moisan, J., Sosik, H.M., Kudela, R., Mouw, C.B., Barnard, A.H., Palacios, S., Roesler, C., Drakou, E.G., Appeltans, W.and Jetz, W., {\it Satellite sensor requirements for monitoring essential biodiversity variables of coastal ecosystems}, Ecological Applications, {\bf 2018}. Vol. 28, issue 3: p. 3984-4001. (\url{https://doi.org/10.1002/eap.1682})

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.2in}
\section{PUBLICATIONS -- PROCEEDINGS}
\vspace{0.05in}
{\bf Concha, J.A.} $\&$ Schott, J., {\it Atmospheric Correction for Landsat 8 over Case 2 Waters}, Proc. SPIE 9607, Earth Observing Systems XX, {\bf 2015}. Vol. 9607. (\url{https://doi.org/10.1117/12.2188345})
\vspace{0.1in}\\
{\bf Concha, J.A.} $\&$ Schott, J., {\it In-water Component Retrieval over Case 2 Water using Landsat 8: Initial Results}, 2014 IEEE Geoscience and Remote Sensing Symposium, {\bf 2014}. pp. 4458-4461 (\url{https://doi.org/10.1109/IGARSS.2014.6947481})
\vspace{0.1in}\\
{\bf Concha, J.A.} $\&$ Schott, J., {\it A Model-based ELM for Atmospheric Correction over Case 2 water with Landsat 8}, Proc. SPIE 9111, Ocean Sensing and Monitoring VI, {\bf 2014}. Vol. 911112 (\url{https://doi.org/10.1117/12.2050589})
\vspace{0.1in}\\
{\bf Concha, J.A.} $\&$ Gerace, A., {\it Atmospheric Compensation for WV2 Satellite and In-Water Component Retrieval}, 2012 IEEE International Geoscience and Remote Sensing Symposium, {\bf 2012}. pp. 2833-2836. (\url{https://doi.org/10.1109/IGARSS.2012.6350842})
\vspace{0.1in}\\
{\bf Concha, J.A.} $\&$ Gerace, A., {\it Atmospheric Compensation for WV2 Satellite and In-Water Component Retrieval}, Proc. SPIE 8390, Algorithms and Technologies for Multispectral, Hyperspectral, and Ultraspectral Imagery XVIII, {\bf 2012}. Vol 8390. (\url{https://doi.org/10.1117/12.918962})\\

\end{resume}



% \vspace{4cm}
% \begin{tabular}{@{}p{4.3in}p{2in}@{}}
% & \hrulefill \\
% \today, Greenbelt, MD, USA \hfill& ~~~Javier A. Concha, Ph.D.\\
% \end{tabular}



\end{document}